---
title: "Markdown #2 - HW"
author: "Cameron Atighetchi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../Output/")
```

# Summary

This is the HW for 03-02-23 where I created a R markdown with at least one list, **bold**, and *italicized* element.  
As well as one plot and one table each with the preloaded *palmerpenguins* package information. 


# Load Libraries  
```{r}
library(tidyverse)
library(here)
library(palmerpenguins)
library(kableExtra)
```

Load all libraries we are using for this lab today

# Creating a **Plot** with *Penguins* Data
```{r PenguinsHW03-02-23}
penguins %>%
  ggplot(aes(x = bill_length_mm, # create a scatter plot grouped by island with different colors for each
          y = bill_depth_mm, 
         color = island,
         group = island)) +
  geom_point()
  
```

# Create a **Table** for *Penguins* Data
```{r, fig.height=3}
penguins %>%
  group_by(island) %>% # groups by island
  select(bill_length_mm, body_mass_g) %>% #selects bill length and body mass columns
  summarise(billmean = mean(bill_length_mm, na.rm = TRUE), # calculates mean for bill length
            bodymean = mean(body_mass_g, na.rm = TRUE)) %>% # calculates mean for body mass
 kbl() %>% # creates a kable table
  kable_styling(full_width = FALSE) #sets width to be 'skinnier' and not span the entire page
  
```

# Creating a List in R Markdown  

Here we are learning how to create a list.  
This list will outline what we do when we come into class **everyday**

  1. Load up R Studio and git pull lecture notes.  
  2. Create a Week # Folder with Output-Script-Data.  
  3. Create starter script introduction.  
  4. Load libraries, Data Wrangle, and Functions  
  5. At end of class: git add, git commit, git push!
  

  
