---
title: 'Lab: Functional Coding'
author: "Cameron Atighetchi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functional Coding -- Lab

## Load Libraries

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(ggrepel)
library(ggthemes)
```

## Load Data

I decided to use the mtcars dataset in base R and focus in on the miles per gallon (mpg)
```{r}
cars_data <- mtcars # assigns a new value to base R mtcars
```

## Non - Plotting Function
I want to use a function to convert miles per gallon (mpg) to kilometers per gallon (kmpg)
```{r}
mpg_to_km_per_gallon <- function(mpg) {
  kmpg <- (mpg * 0.425) # creates a conversion value from mpg to kmpg as a function
  return(kmpg) # returns kmpg value
}
```
### Using our new mpg to kmpg function we can convert all values within the mpg column into kilometers per gallon
```{r}
kmpg_cars <- cars_data %>%
  mutate(mpg = mpg_to_km_per_gallon(mpg))

head(kmpg_cars)
```

## Plotting Function

### For the plotting function I decided to create an ifelse function were cars over and under the kmpg of 9 are plotted in the first plot and all cars are plotted in the second plot

#### Setting the function:
```{r}
myplot<-function(data = kmpg_cars, x, y, mpg = TRUE){ # add new argument for lines
  if(mpg == TRUE){
    ggplot(data, aes(x = {{x}}, y = {{y}} > 9, label = rownames(kmpg_cars)))+
      geom_point()+
      theme_bw()
  }
  else{
    ggplot(data, aes(x = {{x}}, y = {{y}}, label = rownames(kmpg_cars)))+
      geom_point()+
      theme_bw()
  }
}
```

#### Plot set to TRUE (tells us the incidents of Kmpg > 9 or Kmpg < 9)
```{r}
myplot(x = wt, y = mpg, mpg = TRUE) +
  labs(x = "Weight (in thousands of lbs)",
       y = "Kmpg > 9",
       title = "Kmpg > 9 (TRUE) or Kmpg < 9 (FALSE)") +
  theme_clean() +
  geom_label_repel(max.overlaps = Inf)
```


#### Plot set to FALSE (shows us all points plotted)
```{r}
myplot(x = wt, y = mpg, mpg = FALSE) +
  labs(x = "Weight (in thousands of lbs)",
       y = "Kmpg",
       title = "Kmpg as a function of weight of a make and model for Cars")

```

