---
title: "Iterative Coding - Lab"
author: "Cameron Atighetchi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE,
                      message = FALSE)
```

# Iterative Coding - Lab

## Load Libraries

```{r}
library(tidyverse)
library(here)
```

## For Loops

First, we need to define our path & create pattern recognition
```{r}
HWPath<-here("Week_12", "Data", "HW") # creates a path

HW_files <- dir(path = HWPath, pattern = ".csv") # creates a pattern
```

Next, we need to allocate space by making an empty dataset
```{r}
HW_data <- data.frame(matrix(nrow = length(HW_files), ncol = 5)) # creates a dataframe

colnames(HW_data) <- c("filename", "mean_temp", "mean_light", "stdev_temp", "stdev_light") # changes column names
```

Now, we can create our **for loop** using raw data and our mean + stdev functions
```{r}
for (i in 1:length(HW_files)){ 
raw_data<-read_csv(paste0(HWPath,"/",HW_files[i])) # looks within our files
HW_data$filename[i]<-HW_files[i] # gives the filename to our columns
HW_data$mean_temp[i]<-mean(raw_data$Temp.C, na.rm =TRUE) # mean temp code
HW_data$mean_light[i]<-mean(raw_data$Intensity.lux, na.rm =TRUE) #mean light code
HW_data$stdev_temp[i]<-sd(raw_data$Temp.C, na.rm =TRUE) #stdev temp code
HW_data$stdev_light[i]<-sd(raw_data$Intensity.lux, na.rm =TRUE)}#stdev light code

HW_data

```


## Map() Functions

First, we must define our path for using map() functions
```{r}
HW_map_Path<-here("Week_12", "Data", "HW") # create path

HW_map_files <- dir(path = HWPath, pattern = ".csv", full.names = TRUE) #create pattern with full path names
```

Next, we read in the files using map instead of using a for loop
```{r}
HW_map_data <- HW_map_files %>% # assign new value to directory
  set_names() %>% #set's the id for each file
  map_df(read_csv, .id = "filename") %>% #map everything to dataframe and put id in filename column
  group_by(filename) %>% # group by filenames
  summarise(mean_temp = mean(Temp.C, na.rm = TRUE), # compute mean temp
            mean_light = mean(Intensity.lux,na.rm = TRUE), # compute mean light
            stdev_temp = sd(Temp.C, na.rm = TRUE), # compute stdev temp
            stdev_light = sd(Intensity.lux, na.rm = TRUE)) # compute stdev light

HW_map_data
```







