---
title: "Intro to Mapping Lab"
author: "Cameron Atighetchi"
date: '`r Sys.Date()`'
output: 
  prettydoc::html_pretty:
      theme: "cayman"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../Output/")
```

# Summary  

Today we are using Bigfoot data to plot Bigfoot sightings in Alabama!!

# Load Libraries  
```{r}
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
library(prettydoc)
```

Load all libraries we are using for this lab today.  

# Load our Bigfoot Data

```{r}
bigfoot_data<-read_csv(here("Week_07","Data","bigfoot.csv")) # Load our Bigfoot Data
```

Here we are loading our Bigfoot csv data.  

## Filter our Bigfoot data to include States, Latitude and Longitude Data

```{r}
bigfoot_data <- bigfoot_data %>%
  select (state, latitude, longitude) %>%  # select only state, latitude, and longitude columns
  drop_na(state, latitude, longitude) %>%  # filter NAs from state, latitude, and longitude 
  filter(state == "Alabama") # this filters out all values except for Alabama

head(bigfoot_data)

```

## Set up Alabama map using counties data

```{r}

counties <- map_data("county") %>%  # load county map data from 'mapdata' package
  filter (region == "alabama") # filter region to only show alabama
head(counties)

```

## Plot Bigfoot sightings in Alabama on a map

```{r BigfootMapLabStep1}
ggplot() +
  geom_polygon(data = counties, # data is equal to counties w/ higher resolution
               aes(x = long, # set x as longitude
                   y = lat, # set y as latitude
                   group = group), # lifts pen up 
               fill = "black", # fills map black
               color = "#f09892") + # outlines county and state lines with red
  coord_map() + # coordinates map to fit 
  theme_minimal() # minimal theme
```

## Add our Bigfoot sighting points to our map of Alabama  

```{r BigfootMapLabStep2}
# Let's add our points to our map
ggplot() +
  geom_polygon(data = counties,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "black",
               color = "#f09892") +
  coord_map() +
  theme_minimal() +
  geom_point(data = bigfoot_data, # adds points from bigfoot data
             aes(x = longitude,  # x is set to long
                 y = latitude), # y is set to lat
             color = "white")  # plot points as white
```


## Customize our Plot using different themes 

```{r BigfootMapLabStep3}
ggplot() +
  geom_polygon(data = counties,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "black",
               color = "#f09892") +
  coord_map() +
  theme_minimal() +
  geom_point(data = bigfoot_data,
             aes(x = longitude, 
                 y = latitude),
             color = "white") +
  labs(title = "Bigfoot Sightings in Alabama", # adds plot title
       x = "Longitude", # adds x axis title
       y = "Latitude") + # adds y axis title
  theme(plot.title = element_text(hjust = 0.6), # centers plot title
        axis.ticks = element_blank()) #gets rid of scaled axis ticks
  
```


### You've created a Plot!!!!!!!  


